### 2017-10-09 writing/paper/sections/coincidences.tex
Fixes for comments DMTCS

@@

\begin{proposition}[First Dominating Pattern Rule]
    \label{prop:dom1}
    Given two mesh patterns \(m_1 =(\sigma, R_1)\) and \(m_2 = (\sigma, R_2)\),
    and a dominating classical pattern \(\pi = (\pi,\emptyset)\) such that
    \(\setsize{\pi} \le \setsize{\sigma} + 1\), the sets \(\av{\{\pi,m_1\}}\) and
    \(\av{\{\pi,m_2\}}\) are coincident if

    \begin{enumerate}
        \item The mesh set \(R_2 = R_1 \cup \{(a,b)\}\)
        \item \(\pi \preceq \sigma^\boks{a,b}\)\label{prop:dom1:cont}
    \end{enumerate}
\end{proposition}

@@

\begin{proof}[Proof of \PropositionRef{prop:dom1}]
    We need to prove that \(\av{\{\pi,m_1\}} = \av{\{\pi,m_2\}}\).

@@

    Taking both directions of the containment we can therefore draw the
    conclusion that \(\av{\{\pi,m_1\}} = \av{\{\pi,m_2\}}\).
\end{proof}

@@

\subsection{Coincidence classes of Av(\{231, (21, \textit{R})\}).}
By application of \PropositionRef{prop:dom1} we obtain \(43\) coincidence
classes. Experimentation shows that there are in fact at least \(39\) coincidence
classes, for example the following two patterns seem to be coincident in
\(\av{\perm{2,3,1}}\) but this is not explained by \PropositionRef{prop:dom1}.
\begin{equation*}
    m_1 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,2/1} \text{ and } m_2 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,2/1}
\end{equation*}

@@

\begin{proposition}[Second Dominating Pattern Rule]
    \label{prop:dom2}
    Given two mesh patterns \(m_1 =(\sigma, R_1)\) and \(m_2 = (\sigma, R_2)\),
    and a dominating classical pattern \(\pi = (\pi,\emptyset)\) such that
    \(\setsize{\pi} \le \setsize{\sigma} + 2\), the sets \(\av{\{\pi,m_1\}}\) and
    \(\av{\{\pi,m_2\}}\) are coincident if

@@

This proposition essentially states that we slide all of the points in the box we desire
to shade diagonally, and chose the topmost/bottommost point to replace the original
point in the mesh pattern.

@@

\subsection{Coincidence classes of Av(\{231, (12, \textit{R})\}).}
When considering the coincidence classes of \(\av{\{\perm{2,3,1},\mperm{1,2}{R}\}}\)
we first apply the two Dominating Pattern rules previously established.
Starting from \(220\) classes, application of the first Dominating Pattern rule
gives \(85\) classes. Following this with the second Dominating Pattern rule
reduces the number of classes to \(59\). However we know that there are patterns
where the coincidences are not explained by the rules given above.

>>>>

We then form three Propositions called ``Dominating Pattern Rules'', if the First Dominating
Pattern Rule shows that \(q_1 \coinc{\pi} q_2\) then we write \(q_1 \coinc[(1)]{\pi} q_2\).
If a combination of the First and Second Dominating Pattern Rules show that \(\av{p,q_1}= \av{p,q_2}\) then we write \(q_1 \coinc[(2)]{\pi} q_2\); similarly we write \(q_1 \coinc[(3)]{\pi} q_2\) if a combination of all three rules shows coincidences.

@@

\begin{proposition}[First Dominating Pattern Rule]
    \label{prop:dom1}
    Given two mesh patterns \(m_1 =(\sigma, R_1)\) and \(m_2 = (\sigma, R_2)\),
    and a dominating classical pattern \(\pi = (\pi,\emptyset)\) such that
    \(\setsize{\pi} \le \setsize{\sigma} + 1\), then \(m_1 \coinc{\pi} m_2 \) 
    as a consequence of the first dominating pattern rule if
    \begin{enumerate}
        \item The mesh set \(R_2 = R_1 \cup \{(a,b)\}\)
        \item \(\pi \preceq \sigma^\boks{a,b}\)\label{prop:dom1:cont}
    \end{enumerate}
\end{proposition}

@@

\begin{proof}[Proof of \PropositionRef{prop:dom1}]
    We need to prove that \(m_1 \coinc{\pi} m_2\).

@@

    Taking both directions of the containment we can therefore draw the
    conclusion that \(m_1 \coinc{\pi} m_2\).
\end{proof}

@@

\subsection{Coincidence classes of Av(\{231, (21, \textit{R})\}).}
By application of \PropositionRef{prop:dom1} we obtain \(43\) \(\coinc[(1)]{231}\)-coincidence
classes between mesh patterns with \(21\) as an underlying classical pattern.
Experimentation shows that there are \(39 \coinc[comp]{231}\)-coincidence
classes between mesh patterns with \(21\) as an underlying classical pattern, for example the following two patterns seem to be coincident in
\(\av{\perm{2,3,1}}\) but this is not explained by \PropositionRef{prop:dom1}.
\begin{equation*}
    m_1 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,2/1} \text{ and } m_2 = \pattern{}{2,1}{0/0,0/1,0/2,1/0,1/1,2/1}
\end{equation*}

@@

\begin{proposition}[Second Dominating Pattern Rule]
    \label{prop:dom2}
    Given two mesh patterns \(m_1 =(\sigma, R_1)\) and \(m_2 = (\sigma, R_2)\),
    and a dominating classical pattern \(\pi = (\pi,\emptyset)\) such that
    \(\setsize{\pi} \le \setsize{\sigma} + 2\), the sets \(\av{\{\pi,m_1\}}\) and
    \(\av{\{\pi,m_2\}}\) are coincident as a consequence of the Second Dominating Rule if

@@

This proposition essentially states that we slide all of the points in the box we desire
to shade diagonally, and chose the topmost/bottommost point to replace the original
point in the mesh pattern. \FigureRef{fig:d2} show how the cases apply to a general container of \(m_1\) to transform it into a container of \(m_2\) , the circled points are the same points in the permutation.
\begin{figure}
\begin{tikzpicture}
	\modpattern[3]{1,2}{2,1}{0/0,0/1,0/2,1/0,2/1}
	\filldraw (1.33,1.66) circle (1.5pt);
	\filldraw (1.66,1.33) circle (1.5pt);
	\filldraw[pattern=crosshatch dots, pattern color=black!80] (2.1,0.9) rectangle (2.5,0.0);
	\filldraw[pattern=crosshatch dots, pattern color=black!80] (2.5,3) rectangle (2.9 ,2.1);
\end{tikzpicture}
\raisebox{8ex}{\(\coinc{}\)}
\begin{tikzpicture}
	\modpattern[3]{1}{2,1}{0/0,0/1,0/2,1/0,1/1,2/1}
	\filldraw (2.15,0.85) circle (1.5pt);
	\filldraw (2.3,0.7) circle (1.5pt);
	\draw (2.3,0.7) circle (3pt);
	\filldraw[pattern=crosshatch dots, pattern color=black!80] (2.4,0.6) rectangle (2.65,0.0);
	\filldraw[pattern=crosshatch dots, pattern color=black!80] (2.65,3) rectangle (2.9 ,2.1);
\end{tikzpicture}
\caption{A depiction of the second dominating pattern rule using our example patterns.}
\label{fig:d2}
\end{figure}

@@

\subsection{Coincidence classes of Av(\{231, (12, \textit{R})\}).}
When considering the coincidence classes of \(\av{\{\perm{2,3,1},\mperm{1,2}{R}\}}\)
we first apply the two Dominating Pattern rules previously established.
Starting from \(220\) classes, we result in \(85 \coinc[(1)]{231}\)-coincidence classes 
reducing to \(59 \coinc[(2)]{231}\)-coincidence classes, considering mesh patterns with
\(12\) as the underlying classical patterns. However we know that there are patterns
where the coincidences are not explained by the rules given above.

### 2017-10-09 writing/paper/sections/introduction.tex
Fixes for comments DMTCS

In this work we aim to establish some ground in this field by computing
coincidences and Wilf-classes and calculating some of the enumerations of
avoiders of a mesh pattern of length 2 and a classical pattern of length 3. We
begin by establishing coincidences between mesh patterns of length 2 while
avoiding a classical pattern of length 3 by computational methods, which are then
used to establish three ``Dominating Pattern Rules'' as well as some special cases
that can be used to calculate coincidences. We then use these coincidence classes
to calculate Wilf-equivalence classes showing some of the methods used.

>>>>

In this work we aim to establish some ground in this field by computing
coincidences and Wilf-classes and calculating some of the enumerations of
avoiders of a mesh pattern of length 2 and a classical pattern of length 3. We
begin by establishing coincidences between mesh patterns of length 2 while
avoiding a dominating pattern by computational methods, which are then
used to establish three ``Dominating Pattern Rules'' as well as some special cases
that can be used to calculate coincidences.

 We then use these coincidence classes
to calculate Wilf-equivalence classes showing some of the methods used.
